Neural Network Language Models for Automatic Speech Recognition

### 2018-12-10 paper/paper.tex
paper: Citations for Milkolov, Schwenk, etc
paper: Merge results and configuration

\section{Model Configurations}
\label{sec:configuration}

\section{Experimental Results}
\label{sec:results}

@@

@@

\bibitem{cho2014}
  https://arxiv.org/pdf/1406.1078v3.pdf
\end{thebibliography}
\end{document}

>>>>

\section{Model Configurations and Results}
\label{sec:results}

We ran two sets of experiments on each dataset. Because of the difference in sizes
between the Gigaword and WikiText datasets we were able to run more tests on the
WikiText dataset and scale a few of those results up to Gigaword.

@@

\bibitem{Milkolov10}
  Milkolov T., et al, Recurrent neural network based language model, INTERSPEECH 2010

@@

\bibitem{cho2014}
  https://arxiv.org/pdf/1406.1078v3.pdf

\bibitem{schwenk05}
  ftp://tlp.limsi.fr/public/emnlp05.pdf. Accessed 6 Nov. 2018.

\bibitem{hinton2012}
  https://arxiv.org/pdf/1207.0580.pdf

\end{thebibliography}

\end{document}
